Market Simulator

### 2020-08-18 analysis/05_market_simulator.Rmd
trouble shooting to get a reactive value from sliderInput as the value for the beta_persona levels that have rating.

@@

    beta_persona$p1_value[beta_persona$levels == "Political Preference"] = p1_pol_pref()

@@

    # beta_persona$p2_value[beta_persona$levels == '0'] <- 0
    # beta_persona$p2_value[beta_persona$levels == '1'] <- 1
    # beta_persona$p2_value[beta_persona$levels == '2'] <- 2
    # beta_persona$p2_value[beta_persona$levels == '3'] <- 3
    # beta_persona$p2_value[beta_persona$levels == '4'] <- 4
    # beta_persona$p2_value[beta_persona$levels == '5'] <- 5
    # beta_persona$p2_value[beta_persona$levels == '6'] <- 6
    # beta_persona$p2_value[beta_persona$levels == '7'] <- 7

@@

p1_pol_pref <- reactive({
  input$p1_political_pref
})
```

@@

df <- as.data.frame(matrix(rep(0), nrow = 1))

df$levels = "Rating"

df$p1[df$levels == "Rating"] = p1_pol_pref()

p1_pol_pref <- reactive({
  input$p1_political_pref
})

@@

beta_test <- as.data.frame(matrix(rep(0), nrow = 13))

beta_test$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human rights", "Refugee relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")

beta_test$ai_issue <- 0
beta_test$ai_issue[4] <- 1
beta_test$ai_issue[8] <- 1
beta_test$ai_issue[9] <- 1

beta_test$gp_issue <- 0
beta_test$gp_issue[4] <- 1
beta_test$gp_issue[5] <- 1
beta_test$gp_issue[8] <- 1
beta_test$gp_issue[9] <- 1

beta_test$ox_issue <- 0
beta_test$ox_issue[4] <- 1
beta_test$ox_issue[6] <- 1
beta_test$ox_issue[8] <- 1
beta_test$ox_issue[9] <- 1

beta_test$rc_issue <- 0
beta_test$rc_issue[4] <- 1
beta_test$rc_issue[7] <- 1
beta_test$rc_issue[8] <- 1
beta_test$rc_issue[9] <- 1

  ai_exp_util1 <- round(exp(t(beta_test[, 3]) %*% as.matrix(p_beta1)),2)
  gp_exp_util1 <- round(exp(t(beta_test[, 4]) %*% as.matrix(p_beta1)),2)
  ox_exp_util1 <- round(exp(t(beta_test[, 5]) %*% as.matrix(p_beta1)),2)
  rc_exp_util1 <- round(exp(t(beta_test[, 6]) %*% as.matrix(p_beta1)),2)

@@

exp_util2 <- round(exp(t(beta_test[, 4]) %*% as.matrix(p_beta2)),2)

@@

exp_util3 <- round(exp(t(beta_test[, 5]) %*% as.matrix(p_beta3)),2)

@@

  df[,2] <- c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")
  df[,3] <- c(rep("Utility", 4), rep("Market Share", 4))
  df[,4] <- c(rep("Persona 1",8), rep("Persona 2", 8), rep("Persona 3", 8))
  colnames(df) <- c('Value', 'Organization', "Type", "Persona")

@@

@@

sliderInput("p1_political_pref",
       label = "Political views from liberal to conservative:",
       min = 0,
       max = 7,
       value = 0)

>>>>

p1_politic_pref <- reactive({
  input$p1_political_pref
})

@@

    beta_persona$p1_value[beta_persona$levels == "Political Preference"] <- p1_politic_pref()

@@

@@

@@

# df <- as.data.frame(matrix(rep(0), nrow = 1))
# 
# df$levels = "Rating"
#                         
#                         
# df$p1[df$levels == "Rating"] <- input$rating_id
# 
# 
# p1_pol_pref <- reactive({
#   input$p1_political_pref
# })
# 
# 
# sliderInput("rating_id",
#        label = "Rating",
#        min = 0,
#        max = 7,
#        value = 0)

@@

# beta_test <- as.data.frame(matrix(rep(0), nrow = 13))
# 
# beta_test$levels = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross", "Environment", "Human rights", "Refugee relief", "Engages in transparency", "Engages in financial accountability","Handful of wealthy private donors", "Government Grants", "Criticized by government", "Under government crackdown")
# 
# beta_test$ai_issue <- 0
# beta_test$ai_issue[4] <- 1
# beta_test$ai_issue[8] <- 1
# beta_test$ai_issue[9] <- 1
# 
# 
# beta_test$gp_issue <- 0
# beta_test$gp_issue[4] <- 1
# beta_test$gp_issue[5] <- 1
# beta_test$gp_issue[8] <- 1
# beta_test$gp_issue[9] <- 1
# 
# 
# beta_test$ox_issue <- 0
# beta_test$ox_issue[4] <- 1
# beta_test$ox_issue[6] <- 1
# beta_test$ox_issue[8] <- 1
# beta_test$ox_issue[9] <- 1
# 
# beta_test$rc_issue <- 0
# beta_test$rc_issue[4] <- 1
# beta_test$rc_issue[7] <- 1
# beta_test$rc_issue[8] <- 1
# beta_test$rc_issue[9] <- 1
# 
# 
# 
#   ai_exp_util1 <- round(exp(t(beta_test[, 3]) %*% as.matrix(p_beta1)),2)
#   gp_exp_util1 <- round(exp(t(beta_test[, 4]) %*% as.matrix(p_beta1)),2)
#   ox_exp_util1 <- round(exp(t(beta_test[, 5]) %*% as.matrix(p_beta1)),2)
#   rc_exp_util1 <- round(exp(t(beta_test[, 6]) %*% as.matrix(p_beta1)),2)
# 
#   ai_rate1 <- round(100 * ai_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   gp_rate1 <- round(100 * gp_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   ox_rate1 <- round(100 * ox_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))
#   rc_rate1 <- round(100 * rc_exp_util1/sum(ai_exp_util1, gp_exp_util1, ox_exp_util1, rc_exp_util1))

@@

# 
# exp_util2 <- round(exp(t(beta_test[, 4]) %*% as.matrix(p_beta2)),2)

@@

# 
# exp_util3 <- round(exp(t(beta_test[, 5]) %*% as.matrix(p_beta3)),2)

@@

@@

sliderInput("p1_political_pref",
       label = "Political Preference",
       min = 0,
       max = 7,
       value = 0)

@@
